Paper Analysis

### 2025-01-13 Paper_WriteUp/Paper_Plots.qmd
update the colour scheme and make it clear which players are being removed

bullet_data |> nrow()
## average number, we remove the two accounts with 1 and 3 games only
## throughout we do not consider those who play less than 10 games
## at a given format when fitting any model
bullet_data |> 
  group_by(Username) |> 
  count() |> 
  filter(n > 3) |>
  ungroup() |> 
  summarise(avg = mean(n))

@@

@@

hist_comp_global <- bind_rows(prev_pars, pre_10_pars) |> 
  ggplot(aes(x = value, color = model)) +
  stat_pointinterval(position = position_dodge(width = 0.2)) +
  facet_wrap(~name,
             scales = "free",
             labeller = labeller(name = facet_labels)) +
  labs(x = element_blank(), y = element_blank(), color = element_blank()) +
  theme_3col() +
  theme(legend.position = "bottom") +
  scale_x_continuous(breaks = breaks_pretty(n = 2)) +
  scale_color_viridis_d(option = "D")

@@

bul_blit_gm_comp_global <- bind_rows(bullet_pars, blitz_pars) |> 
  ggplot(aes(x = value, y = name, color = model)) +
  stat_pointinterval(position = position_dodge(width = 0.2)) +
  facet_wrap(~name,
             scales = "free",
             labeller = labeller(name = facet_labels)) +
  labs(x = element_blank(), y = element_blank(), color = element_blank()) +
  theme_3col() +
  theme(legend.position = "bottom") +
  scale_x_continuous(breaks = breaks_pretty(n = 2)) +
  scale_color_viridis_d(option = "D")

@@

comp_gm_winner <- player_pars_bullet |> 
  filter(param == 2) |> 
  mutate(y = reorder(player_name, value, FUN = median)) |> 
  bind_rows(player_pars_blitz |> 
              filter(param == 2) |> 
              mutate(y = as.factor(player_name))) |> 
  ggplot(aes(x = value, y = y,
             color = model)) +
  stat_pointinterval(position = position_dodge(width = 1)) +
  labs(x = element_blank(), y = element_blank(), color = element_blank()) +
  theme_single_y() +
  theme(legend.position = "bottom") +
  scale_x_continuous(breaks = breaks_pretty(n = 3)) +
  scale_color_viridis_d(option = "D")

>>>>

bullet_data |> nrow()
## average number, we remove the two accounts with 1 and 3 games only
## throughout we do not consider those who play less than 10 games
## at a given format when fitting any model
bullet_data |> 
  group_by(Username) |> 
  count() |> 
  filter(n > 10) |> # remove 2 players with <10 games
  ungroup() |> 
  summarise(avg = mean(n))

@@

## count how many blitz games they play as comparison

blitz_data |> 
  group_by(Username) |> 
  count() |> 
  filter(n > 10) |> # remove players with < 10 games
  ungroup() |> 
  summarise(avg = mean(n))

@@

hist_comp_global <- bind_rows(prev_pars, pre_10_pars) |> 
  ggplot(aes(x = value, color = model)) +
  stat_pointinterval(position = position_dodge(width = 0.2)) +
  facet_wrap(~name,
             scales = "free",
             labeller = labeller(name = facet_labels)) +
  labs(x = element_blank(), y = element_blank(), color = element_blank()) +
  theme_3col() +
  theme(legend.position = "bottom") +
  scale_x_continuous(breaks = breaks_pretty(n = 2)) +
  scale_color_viridis_d(option = "H")

@@

bul_blit_gm_comp_global <- bind_rows(bullet_pars, blitz_pars) |> 
  ggplot(aes(x = value, y = name, color = model)) +
  stat_pointinterval(position = position_dodge(width = 0.2)) +
  facet_wrap(~name,
             scales = "free",
             labeller = labeller(name = facet_labels)) +
  labs(x = element_blank(), y = element_blank(), color = element_blank()) +
  theme_3col() +
  theme(legend.position = "bottom") +
  scale_x_continuous(breaks = breaks_pretty(n = 2)) +
  scale_color_viridis_d(option = "H")

@@

comp_gm_winner <- player_pars_bullet |> 
  filter(param == 2) |> 
  mutate(y = reorder(player_name, value, FUN = median)) |> 
  bind_rows(player_pars_blitz |> 
              filter(param == 2) |> 
              mutate(y = as.factor(player_name))) |> 
  ggplot(aes(x = value, y = y,
             color = model)) +
  stat_pointinterval(position = position_dodge(width = 1)) +
  labs(x = element_blank(), y = element_blank(), color = element_blank()) +
  theme_single_y() +
  theme(legend.position = "bottom") +
  scale_x_continuous(breaks = breaks_pretty(n = 3)) +
  scale_color_viridis_d(option = "H")
